\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.75in]{geometry}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{noto}

\definecolor{primary}{RGB}{0, 102, 204}
\hypersetup{colorlinks=true, urlcolor=primary, linkcolor=primary}

\titleformat{\section}{\large\bfseries\color{primary}}{\thesection}{1em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{1em}{}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

\begin{document}

\begin{center}
    {\Huge\bfseries Anupam Jha} \\[0.2cm]
    Web Developer \& AI Prompt Engineer \\[0.1cm]
    \href{mailto:killerboy99126@gmail.com}{killerboy99126@gmail.com} $|$ +91 8700794628 $|$ New Delhi, Mundka \\[0.1cm]
    \href{https://github.com/AkaTriggered}{GitHub} $|$ \href{https://x.com/AkaTriggered}{Twitter} $|$ \href{https://instagram.com/anupamnotfound}{Instagram} $|$ \href{https://youtube.com/@AkaTriggered}{YouTube}
\end{center}

\section*{Professional Summary}
Passionate web developer with over 5 years of experience in creating responsive, user-friendly websites and applications. Skilled in front-end and back-end development, UI/UX design, and AI prompt engineering to optimize interactions with large language models. Enthusiastic about exploring new technologies and building innovative solutions.

\section*{Skills}
\begin{itemize}[leftmargin=*,itemsep=2pt]
    \item \textbf{Frontend Development}: HTML, CSS, JavaScript, Tailwind CSS
    \item \textbf{Backend Development}: Node.js, Express, Python, MySQL, MongoDB
    \item \textbf{AI Prompt Engineering}: Crafting precise prompts for AI models, optimizing outputs for natural language processing tasks
    \item \textbf{Responsive Design}: Cross-device compatibility and adaptive layouts
    \item \textbf{UI/UX Design}: Wireframing, prototyping, user-centered design
    \item \textbf{SEO Optimization}: Enhancing website visibility and search engine rankings
    \item \textbf{Tools \& Platforms}: Git, GitHub, VS Code, IntelliJ IDEA Community Edition
\end{itemize}

\section*{Professional Experience}
\subsection*{Web Developer \& AI Prompt Engineer}
\textbf{Freelance} $|$ New Delhi, India $|$ 2020--Present
\begin{itemize}[leftmargin=*,itemsep=2pt]
    \item Developed responsive websites and web applications using modern frameworks and technologies.
    \item Designed and implemented intuitive UI/UX for enhanced user engagement.
    \item Engineered AI prompts to improve efficiency and accuracy of AI-driven solutions, including chatbots and content generation tools.
    \item Optimized websites for SEO, increasing organic traffic by 30\% for client projects.
    \item Collaborated with clients to deliver tailored solutions meeting specific requirements.
\end{itemize}

\subsection*{Junior Web Developer}
\textbf{Tech Startup (Confidential)} $|$ New Delhi, India $|$ 2018--2020
\begin{itemize}[leftmargin=*,itemsep=2pt]
    \item Built and maintained e-commerce platforms with secure checkout and product management systems.
    \item Contributed to back-end development using Node.js and MongoDB for scalable APIs.
    \item Assisted in creating wireframes and prototypes for new features, improving user satisfaction by 20\%.
\end{itemize}

\section*{Projects}
\begin{itemize}[leftmargin=*,itemsep=2pt]
    \item \textbf{JobVibe} (\href{https://akatriggered.github.io/JobVibe/#home}{Live Demo}, \href{https://github.com/AkaTriggered/JobVibe}{GitHub})
    \begin{itemize}[leftmargin=*,itemsep=1pt]
        \item Developed a job listing platform for government jobs in India with real-time RSS feed updates and animated UI.
        \item Technologies: HTML, CSS, JavaScript, RSS Feeds.
    \end{itemize}
    \item \textbf{Portfolio Website} (\href{https://github.com/AkaTriggered}{GitHub})
    \begin{itemize}[leftmargin=*,itemsep=1pt]
        \item Created a modern portfolio with responsive design, animations, and contact form.
        \item Technologies: HTML, CSS, JavaScript.
    \end{itemize}
    \item \textbf{AI Prompt Optimization Tool}
    \begin{itemize}[leftmargin=*,itemsep=1pt]
        \item Designed prompts to enhance AI model performance for content generation and task automation.
        \item Technologies: Python, NLP frameworks.
    \end{itemize}
\end{itemize}

\section*{Education}
\textbf{10th Grade (CBSE)} \\
[School Name], New Delhi, India $|$ Year of Completion: [Year] \\
\textbf{12th Grade (CBSE, Current Student)} \\
[School Name], New Delhi, India $|$ Expected Completion: [Year]

\section*{Hobbies}
Exploring the tech world, experimenting with new AI models, and creating innovative websites and applications.

\end{document}